Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-14 paper.tex
model selection

\subsection{Estimators}

@@

\textcolor{red}{TODO: rewrite and briefly describe the API (see user guide)}\\
\textcolor{red}{TODO: describe Scorer API?}\\
\textcolor{red}{TODO: mention that GridSearchCV objects are themselves estimators}
\textcolor{red}{TODO: Talk about nested attribute syntax.}

The aforementioned \texttt{Pipeline} object
can be passed as an argument to a model selection algorithm.
Available algorithms at the time of writing include random search
\citep{bergstra2012} and ``grid search''.
The latter, which we shall use in this example,
performs an exhaustive search through a grid formed by the cartesian product
of a set of possible values for each parameter, specified by the user.
In our example, this grid might be given as:

\begin{align*}
         & \textsf{stopwords} \in \{0, 1\}                      \\
  \times & \; \textsf{tf} \in \{\textsf{linear}, \textsf{log}\} \\
  \times & \; n_\textsf{features} \in \{1000, 2000, 5000\}      \\
  \times & \; \textsf{norm} \in \{\ell_1, \ell_2\}              \\
  \times & \; C \in \{10, 100, 1000\}
\end{align*}

At each point in this grid, $k$-fold cross validation is run
to estimate the performance of the estimator according to some measure
(e.g., accuracy, $F_\beta$-score or a host of clustering quality metrics)
and the best performing set of hyperparameters is stored
on the \texttt{GridSearchCV} object, again, as a public attribute.

>>>>

\subsection{Estimators}
\label{sec:estimators}

@@

As introduced in Section~\ref{sec:estimators}, hyper-parameter values set in the
constructor of an estimator determine its behavior. In particular, depending on
the problem, some values produce estimators that are better than others. In this
setting, the problem of \textit{model selection} consists in finding, within
some hyper-parameter space, the combination of hyper-parameter values yielding
an estimator whose performance optimizes some score function on unseen data. For
example, in the case of a decision tree, too small values for the
\texttt{max\_depth} parameter will make the tree to underfit while too large
values will make the tree to overfit the training data. The problem is therefore
to find the best trade-off value in order to maximize the performance of the
tree on unseen data.

In \sklearn, both \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} meta-estimators
implement model selection. They take as inputs an estimator (basic or
complex), a grid of hyper-parameter values, a cross-validation scheme and a
score function. At \texttt{fit}, a \texttt{GridSearchCV} object generates
exhaustively all hyper-parameter combinations from the grid, while a
\texttt{RandomizedSearchCV} instance generates a limited number of combinations
randomly sampled from the grid. Then, for each combination, the meta-estimator
fits the given estimator with the corresponding hyper-parameter values and
evaluates its performance through the given cross-validation scheme. Finally,
the best performing model is retained and exposed as a public attribute.

From an API point of view, cross-validation schemes are given as iterator
objects over train and test folds on the training data. The library provides
various such iterators, including K-Fold, Leave-One-Out or shuffled
cross-validation schemes. The score function used by default is the function
provided by the estimator itself. However, the library provides a variety of
score functions that can be used instead, including -- among many others --
accuracy, AUC or $F_\beta$-score for classifiers; $R^2$ score or mean squared
error for regressors; or the Rand Index for clustering estimators. Also, let us
note that \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} instances are
themselves estimators. In particular, they provide \texttt{predict},
\texttt{predict\_proba}, \texttt{transform} and \texttt{score} methods that are
all transparently delegated to the best estimator found during \texttt{fit}.

As an example, the snippet below illustrates how to optimize the hyper-parameter
values of an SVM classifier. It considers an exhaustive exploration of all
hyper-parameter combinations from two distinct grids of parameter values and
maximizes the AUC of the classifier through a 10-fold cross-validation:
\begin{verbatim}
    from sklearn.svm import SVC
    from sklearn.grid_search import GridSearchCV

    param_grid = [
      {'C': [1, 10, 100, 1000], 'kernel': ['linear']},
      {'C': [1, 10, 100, 1000], 'gamma': [0.001, 0.0001], 'kernel': ['rbf']},
    ]

    clf = GridSearchCV(SVC(), param_grid, scoring="roc_auc", cv=10)
    clf.fit(X_train, y_train)
\end{verbatim}

\textcolor{red}{TODO: Mention that pipelines can also be grid-searched.}
